14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-19 rules/rules19.tex
Rules: Try different layout for input/output.

\newcommand{\akey}[1]{\texttt{#1}}

@@

\header{Input and output.}
%
In the \emph{\inctrack}, the \emph{trace executor} will send commands from an
(incremental) benchmark file to the standard input channel of the solver.  In
\emph{all other tracks}, a participating solver must read a \emph{single}
benchmark file, whose filename is presented as the first command-line argument
of the solver.

Benchmark files are in the concrete syntax of the SMT-LIB format
version~2.6, though with a \emph{restricted} set of commands.  A benchmark
file is a text file containing a sequence of SMT-LIB commands that
satisfies the following requirements:
%
\begin{enumerate}
  \item
    \begin{enumerate}
      \item In the \textbf{\maintrack} and \textbf{\ucoretrack}, there may be a single
      \akey{(set-option :print-success ...)} command.  Note that
      \texttt{success} outputs are ignored by the post-processor used by
      the competition.\footnote{SMT-LIB~2.6 requires solvers to produce
        a \texttt{success} answer after each \akey{set-logic},
        \akey{declare-sort}, \akey{declare-fun} and \akey{assert}
        command (among others), unless the option \akey{:print-success}
        is set to false.  Ignoring the \texttt{success} outputs allows
        for submitting fully SMT-LIB~2.6 compliant solvers without the
        need for a wrapper script, while still allowing entrants of
        previous competitions to run without changes.}
      \item In the \textbf{\inctrack}, the \akey{:print-success} option
      must not be disabled.  The trace executor will send an initial
        \akey{(set-option :print-success true)} command to the solver.
      \item In the \textbf{\ucoretrack}, there is a single \akey{(set-option
        :produce-unsat-cores true)} command.
    \end{enumerate}
  \item A (single) \akey{set-logic} command is the \emph{first} command after
    any \akey{set-option} commands.
  \item It may contain any number of \akey{set-info} commands.
  \item It may contain any number of \akey{declare-sort} and
    \akey{define-sort} commands.  All sorts declared or defined with
    these commands must have zero arity.
  \item It may contain any number of \akey{declare-fun} and \akey{define-fun}
    commands.
  \item If the logic features algebraic datatypes, the benchmark file may
    contain any number of \akey{declare-datatype(s)} commands.
  \item It may contain any number of \akey{assert} commands.  All formulas in
    the file belong in the declared logic, with any free symbols declared in
    the file.
  \item
    \begin{enumerate}
      \item In \textbf{all} tracks \textbf{except} the \ucoretrack,  named
        terms (i.e., terms with the \akey{:named} attribute) are \emph{not}
        used.
      \item In the \textbf{\ucoretrack}, top-level assertions may be named.
    \end{enumerate}
  \item
    \begin{enumerate}
      \item In \textbf{all} tracks \textbf{except} the \inctrack, there is
        \emph{exactly one} \akey{check-sat} command.
      \item In the \textbf{\inctrack}, there are one or more
      \akey{check-sat} commands.  There may also be zero or more
      \akey{push 1} commands, and zero or more \akey{pop 1} commands,
      consistent with the use of those commands in the SMT-LIB standard.
    \end{enumerate}
  \item In the \textbf{\ucoretrack}, the \akey{check-sat} command (which is
    always issued in an unsatisfiable context) is followed by a single
    \akey{get-unsat-core} command.
  \item In the \textbf{\mvaltrack}, the \akey{check-sat} command (which is
    always issued in a satisfiable context) is followed by a single
    \akey{get-model} command.
  \item It may \emph{optionally} contain an \akey{exit} command as its
    last command.  In the \textbf{\inctrack}, this command must not be
    omitted.
  \item No other commands besides the ones just mentioned may be used.
\end{enumerate}
%
The SMT-LIB format specification is available from the ``Standard''
section of the SMT-LIB website~\cite{SMT-LIB}.  Solvers will be given
formulas only from the divisions into which they have been entered.

>>>>

\newcommand{\akey}[1]{\textbf{#1}}
\newcommand{\bkey}[1]{\textbf{\texttt{#1}}}

@@

\header{Input and Output.}
%
In the \emph{\inctrack}, the \emph{trace executor} will send commands from an
(incremental) benchmark file to the standard input channel of the solver.  In
\emph{all other tracks}, a participating solver must read a \emph{single}
benchmark file, whose filename is presented as the first command-line argument
of the solver.

Benchmark files are in the concrete syntax of the SMT-LIB format
version~2.6, though with a \emph{restricted} set of commands.  A benchmark
file is a text file containing a sequence of SMT-LIB commands that
satisfies the following \emph{requirements}:
%
\begin{enumerate}
  \item
    \bkey{(set-option :print-success ...)}
    \begin{enumerate}
      \vspace{-1ex}
      \item In the \textbf{\maintrack} and \textbf{\ucoretrack}, there may be a
        single \akey{set-option} command.  Note that \texttt{success} outputs
        are ignored by the post-processor used by the
        competition.\footnote{SMT-LIB~2.6 requires solvers to produce a
        \texttt{success} answer after each \akey{set-logic},
        \akey{declare-sort}, \akey{declare-fun} and \akey{assert} command
        (among others), unless the option \akey{:print-success} is set to
        false.  Ignoring the \texttt{success} outputs allows for submitting
        fully SMT-LIB~2.6 compliant solvers without the need for a wrapper
        script, while still allowing entrants of previous competitions to run
        without changes.}
      \item In the \textbf{\inctrack}, the \akey{:print-success} option
      must not be disabled.  The trace executor will send an initial
        \akey{(set-option :print-success true)} command to the solver.
      \item In the \textbf{\ucoretrack}, there is a single \akey{(set-option
        :produce-unsat-cores true)} command.
    \end{enumerate}
  \item \bkey{(set-logic ...)}\\
    A (single) \akey{set-logic} command is the \emph{first} command after
    any \akey{set-option} commands.
  \item \bkey{(set-info ...)}\\
    A benchmark file may contain any number of \akey{set-info} commands.
  \item \bkey{(declare-sort ...)}\\
    A benchmark file may contain any number of \akey{declare-sort} and
    \akey{define-sort} commands.  All sorts declared or defined with these
    commands must have zero arity.
  \item \bkey{(declare-fun ...)} and \bkey{(define-fun ...)}\\
    A benchmark file may contain any number of \akey{declare-fun} and
    \akey{define-fun} commands.
  \item \bkey{(declare-datatype ...)} and \bkey{(declare-datatypes ...)}\\
    If the logic features algebraic datatypes, the benchmark file may
    contain any number of \akey{declare-datatype(s)} commands.
  \item \bkey{(assert ...)}\\
    A benchmark file may contain any number of \akey{assert} commands.  All
    formulas in the file belong in the declared logic, with any free symbols
    declared in the file.
  \item
    \bkey{:named}
    \begin{enumerate}
      \vspace{-1ex}
      \item In \textbf{all} tracks \textbf{except} the \ucoretrack,  named
        terms (i.e., terms with the \akey{:named} attribute) are \emph{not}
        used.
      \item In the \textbf{\ucoretrack}, top-level assertions may be named.
    \end{enumerate}
    \item
      \bkey{(check-sat)}
      \begin{enumerate}
        \vspace{-1ex}
        \item In \textbf{all} tracks \textbf{except} the \inctrack, there is
          \emph{exactly one} \akey{check-sat} command.
        \item In the \textbf{\inctrack}, there are one or more
        \akey{check-sat} commands.  There may also be zero or more
        \akey{push 1} commands, and zero or more \akey{pop 1} commands,
        consistent with the use of those commands in the SMT-LIB standard.
    \end{enumerate}
    \item \bkey{(get-unsat-core)}\\
    In the \textbf{\ucoretrack}, the \akey{check-sat} command (which is
      always issued in an unsatisfiable context) is followed by a single
      \akey{get-unsat-core} command.
    \item \bkey{(get-model)}\\
      In the \textbf{\mvaltrack}, the \akey{check-sat} command (which is
      always issued in a satisfiable context) is followed by a single
    \akey{get-model} command.
  \item \bkey{(exit)}\\
    It may \emph{optionally} contain an \akey{exit} command as its
    last command.  In the \textbf{\inctrack}, this command must not be
    omitted.
  \item No other commands besides the ones just mentioned may be used.
\end{enumerate}
%
The SMT-LIB format specification is available from the ``Standard''
section of the SMT-LIB website~\cite{SMT-LIB}.  Solvers will be given
formulas only from the divisions into which they have been entered.
